I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-24 Paper/introduction.tex

On such complex DNNs, PRIMA and $\alpha$-$\beta$ CROWN resort to a "refined" path, where the bounds {\em on the first few layers} are refined \cite{MILP2} using an exact MILP encoding. In our algorithm, we do not use an exact encoding but a partial one with the most important ReLU nodes obtained by considering the compensation strength. As it is more efficient, this can be pushed to all layers. This would be infeasible without the selection based on the compensation. The refined version of $\alpha$-$\beta$ CROWN is particularly accurate on small DNNs. As the depth grows, the more work is left to BaB and our algorithm is more accurate, lowering the gap of verified images to the upper bound \cite{attack} down from 
$20\%$ to $16.2\%$ and from $17.6\%$ to $12\%$ (depth 8, Table \ref{tab:example}). On larger naturally learnt DNNs (3000 neurons), BaB only verifies $18.5\%$ more images than DeepPoly (PRIMA only $6.5\%$), while our algorithm verifies $39\%$ more images than DeepPoly (Table \ref{tab:example3}).

>>>>

On such complex DNNs, PRIMA and $\alpha$-$\beta$ CROWN resort to a "refined" path, where the bounds {\em on the first few layers} are refined \cite{MILP2} using an exact MILP encoding. In our algorithm, we do not use an exact encoding but a partial one with the most important ReLU nodes obtained by considering the compensation strength. As it is more efficient, this can be pushed to all layers. This would be infeasible without the selection based on the compensation. The refined version of $\alpha$-$\beta$ CROWN is particularly accurate on small DNNs. As the depth grows, the more work is left to BaB and our algorithm is more accurate, lowering the gap of verified images to the upper bound \cite{attack} down from 
$20\%$ to $16.2\%$ and from $17.6\%$ to $10.9\%$ (depth 8, Table \ref{tab:example}). On larger naturally learnt DNNs (3000 neurons), BaB only verifies $18.5\%$ more images than DeepPoly (PRIMA only $6.5\%$), while our algorithm verifies $39\%$ more images than DeepPoly (Table \ref{tab:example3}).
